\documentclass[11pt]{article}
%\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{ragged2e}
%\textheight=10in
\pagestyle{empty}
%\raggedbottom
\usepackage{hyperref}
\usepackage{microtype}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=cyan,
}
\urlstyle{same}
\raggedright
\usepackage{fullpage}

\addtolength{\oddsidemargin}{-.2in}
\addtolength{\evensidemargin}{-.2in}
\addtolength{\textwidth}{.4in}

%\setlength{\topmargin}{2in}

\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.5in}

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newcommand{\tab}{\hspacet *{2em}}

\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} \hfill #2\\ \textbf{\emph{#3}}\\  }}
\newcommand{\employerwithguide}[4]{{ \textbf{#1} \hfill(#2)\\ \textbf{\emph{#3}}\\ \emph{#4}  }}
\newcommand{\project}[3]{{ \textbf{#1} (#2)\\ \emph{#3}\\  }}
\newcommand{\projectnoguide}[2]{{ \textbf{#1} (#2)\\  }}
\newcommand{\contact}[2]{
%\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
%#2 \lineunder
#2
\end{center}
\vspace*{-8pt}
}
\newcommand{\sbt}{\,\begin{picture}(-1,1)(-1,-3)\circle*{2}\end{picture}\ }
\newcommand{\lbt}{\,\begin{picture}(-1,1)(-1,-3)\circle*{3}\end{picture}\ }
\newenvironment{achievements}{
    \begin{list}{$\lbt$}{
        \topsep 0pt
        \itemsep 0pt
        \addtolength{\leftmargin}{-0.1in}
    }
}
{
    \vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses}[4]{
 \textbf{#1} \hfill{#2}\\
    #3\\
\vspace*{5pt}
}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\
#4 \\
}
\newcommand{\visiting}[4]{
	\textit{#1} \hfill{#2}\\
	#3\\
	\vspace*{5pt}
}



% END RESUME DEFINITIONS

\begin{document}

\pagenumbering{gobble}

\small
\smallskip
\vspace*{-35pt}

\contact{Ryu Matsuura}
{ryumatsuura@u.northwestern.edu $\sbt$ \url{https://ryumatsuura.github.io}}

%%%%%%%%%%%%
%% EDUCATION
%%%%%%%%%%%%

\header{\textbf{Education}}
\schoolwithcourses{Northwestern University}{2019--\textit{present}}{\hspace{2mm} Ph.D. in Economics}

\schoolwithcourses{Northwestern University}{2020}{\hspace{2mm} M.A. in Economics}

\schoolwithcourses{Colby College}{2017}{\hspace{2mm} B.A. in Economics (\textit{Honors \& Distinction}) and Mathematical Science (\textit{Distinction)}, \textit{Summa Cum Laude}}
\hfill{}

\schoolwithcourses{\underline{Visit}: \textnormal{University of Oxford (2015-16), Imperial Business School (2024)}}{}{~\vspace{-3mm}}\hfill{}


%%%%%%%%%%%%%%%%
%% WORKING PAPERS
%%%%%%%%%%%%%%%%

\header{\textbf{Job Market Paper}}

\schoolwithcourses{Political Implications of Trade Liberalization: Evidence from India \textnormal{(with Sebastian J\"{a}vervall and Roza Khoban)}}{}{\vspace{2mm} Individual identity is strongly correlated with their economic outcomes. In societies where ethnicity and economic class largely overlap, marginalized groups face economic disadvantages. While trade theory and empirical evidence suggest that marginalized groups are more likely to support trade reforms, trade liberalization does not necessarily lead to an improvement in economic prosperity of marginalized groups in developing countries. This paper investigates how changes in the economic environment induced by trade liberalization affected voting behaviors and political representation of marginalized groups in India. Using exogenous variation in tariff reductions during India’s trade liberalization in the 1990s and constructing a novel match between politicians and social communities in India, we show that the trade reform significantly shaped both the economic structures and political power dynamics. In particular, we first find that trade liberalization did not lead to an increase in total earnings nor decline in unemployment rate among workers from marginalized groups. We then document that increased exposure to import competition had positive impacts on the vote share and political representation of marginalized groups. We show the suggestive evidence that trade liberalization induced the rise of identity politics.}

\vspace{1mm}

\header{\textbf{Working Papers}}

\schoolwithcourses{Harnessing Satellite Data to Improve Social Assistance Targeting in the Eastern Caribbean \textnormal{(with Sophia Chen, Flavien Moreau, and Joana Pereira)}}{}{\vspace{2mm} Prioritizing populations most in need of social assistance is an important policy decision. In the Eastern Caribbean, social assistance targeting is constrained by limited data and the need for rapid support in times of large economic and natural disaster shocks. We leverage recent advances in machine learning and satellite imagery processing to propose an implementable strategy in the face of these constraints. We show that local well-being can be predicted with high accuracy in the Eastern Caribbean region using satellite data and that such predictions can be used to improve targeting by reducing aggregation bias, better allocating resources across areas, and proxying for information difficult to verify. \vspace{2mm}}

\schoolwithcourses{Political (Mis)selection: The Role of Historical Institutions \textnormal{(with Shubhro Bhattacharya and Utsav Manjeer)}}{}{\vspace{2mm} Is there a persistent impact of historical institutions on the selection of ``bad'' politicians? In this paper, we document the nuanced consequences of history on modern adverse political selection using variations in colonial land tenure systems during British rule in India. Politicians with criminal charges are significantly more likely to run for office, and win elections, in areas where extractive landlords historically held substantial property rights. Corrupt politicians who experience disproportionately large private financial gains in office, however, are significantly more likely to be in areas where individual cultivators historically held property rights. Our analysis establishes that these estimates are not biased by endogeneity concerns. Rather, a plausible mechanism indicates a comparative advantage for criminal politicians in the conflictual electoral environment of landlord areas. The relatively less competitive elections in non-landlord areas, instead, are susceptible to elite capture and subsequent wealth accumulation via corporate connections by politicians.}  

\vspace{1mm}


%%%%%%%%%%%%%%
%% PUBLICATIONS
%%%%%%%%%%%%%%

\header{\textbf{Publications}}
\schoolwithcourses{Development Research at High Geographic Resolution: An Analysis of Night Lights, Firms, and Poverty in India Using the SHRUG Open Data Platform \textnormal{(with Sam Asher, Toby Lunt, and Paul Novosad), \textit{World Bank Economic Review} (2021)}}{}{~\vspace{-3mm}}  

\schoolwithcourses{Shifted Baselines Reduce Willingness to Pay for Conservation \textnormal{(with Loren McClenachan, Shah Payal, and Sahan Dissanayake), \textit{Frontiers in Marine Science} (2018)}}{}{~\vspace{-3mm}} 

%\schoolwithcourses{The Proposed Park in Maine's North Woods: Preferences of Out-of-State Visitors \textnormal{(with Sahan Dissanayake and Andrew Meyer), \textit{Maine Policy Review} (2016)}}{}{~\vspace{0mm}} 
\hfill{}

\newpage

%%%%%%%%%%%%%%%%
%% WORK IN PROGRESS
%%%%%%%%%%%%%%%%

\header{\textbf{Work in Progress}}

\schoolwithcourses{Market Integration and Cost of Borders in Africa \textnormal{(with Robin Burgess, Ameet Morjaria, and Gerard Padr\'{o} i Miquel)}}{}{~\vspace{-3mm}}

\schoolwithcourses{Weather Shocks and Production Outcomes of Firms in Uganda \textnormal{(with Anton Reinicke and Yasuka Tateishi)}}{}{~\vspace{-3mm}}{}

%\schoolwithcourses{Populism and Public Services Delivery}{}{~\vspace{0mm}}  


%%%%%%%%%%%%%%
%% RESEARCH EXP
%%%%%%%%%%%%%%

\header{\textbf{Research Experience}}
\schoolwithcourses{International Monetary Fund}{2023}{\hspace{2mm} Summer Intern in Western Hemisphere Department}

\schoolwithcourses{Northwestern University}{2022-2023}{\hspace{2mm} Research Assistant for Professor Ameet Morjaria}

\schoolwithcourses{Development Data Lab}{2017-2019}{\hspace{2mm} Research Associate}
\hfill{}
\vspace{1mm}

%%%%%%%%%%%%%%
%% TEACHIING EXP
%%%%%%%%%%%%%%

\header{\textbf{Teaching Experience}}
\schoolwithcourses{Northwestern University}{}{\hspace{2mm} Introduction to Microeconomics \hfill 2023}

\schoolwithcourses{Colby College}{}{\hspace{2mm} Statistics for Economics \hfill 2017 \\ \hspace{2mm} Microeconomic Theory \hfill 2015}
\hfill{}
\vspace{1mm}

%%%%%%%%%%%%%%%
%% PRESENTATIONS
%%%%%%%%%%%%%%%

\header{\textbf{Presentations}}
\vspace{1mm}

\begin{tabular}{l @{\hspace{10ex}} l }
	2024 & 4\textsuperscript{th} Early Career Workshop in Quantitative Political Economy, 6\textsuperscript{th} QMUL Economics and Finance \\
	& Workshop for PhD \& Post-doctoral Students, Lewis Lab Graduate Student Workshop \\
	2023 & Pathways to Development Conference \\
	2022 & Society for Institutional \& Organizational Economics, European Meeting of Urban Economics \\
	& Association, Infra4Dev Conference \\
	2017 & Maine Economic Conference \\
	2016 & Heartland Environmental and Resource Economic Workshop  \\
\end{tabular}
\vspace{1mm}
\hfill{}



%%%%%%%%%%
%% GRANTS
%%%%%%%%%%

\header{\textbf{Grants, Scholarship, \& Awards}}
\vspace{1mm}

\begin{tabular}{l @{\hspace{4.5ex}} l }
2023 & Weiss Fund, with Anton Reinicke and Yasuka Tateishi (\$10,000) \\
& International Growth Centre Small Research Grant, with Anton Reinicke and Yasuka Tateishi \\
& (£6,000) \\
& Private Enterprise Development in Low-Income Countries Exploratory Research Grant, with \\
 & Anton Reinicke and Yasuka Tateishi (£10,000) \\
2021-2024 & Japan Student Service Organization Scholarship \\
2019-2021 & Japan-IMF Scholarship \\
2017 & Breckenridge Prize (highest GPA among senior economic majors) \\
& Phi Beta Kappa (top 9\% of senior class) \\
2016 & Economics Department Prize for Junior with Highest GPA \\
& Leslie Dougherty Biddle '89 and George Biddle Fund for International Service Learning, \\
& Internships, and Research \\
\end{tabular}
\vspace{1mm}
\hfill{}


%%%%%%%%%%%%
%% REFERRING
%%%%%%%%%%%%

\header{\textbf{Refereeing}}
\vspace{1mm}

\begin{tabular}{l @{\hspace{0ex}} l }
	\textit{World Bank Economic Review}
\end{tabular}
\vspace{2mm}
\hfill{}
\vspace{1mm}

%%%%%%%%%%%%%%%%%%
%% SKILLS
%%%%%%%%%%%%%%%%%%

\header{\textbf{Skills}}
\vspace{1mm}

\begin{tabular}{l @{\hspace{4.5ex}} l }
	Programming: & Python (advanced), R (intermediate), SQL (beginner), HTLM/CCS (beginner) \\ 
	Software: & MATLAB (advanced), Stata (advanced), QGIS (advanced) \\
	Tools: & Git/Github, Unit Shell, VS Code, Google Maps API, OpenAI API, Micosoft Office
\end{tabular}
\vspace{2mm}
\hfill{}
\vspace{1mm}

%%%%%%%%%%%%%%%%%%
%% PROFESSRIONAL ACT
%%%%%%%%%%%%%%%%%%

\header{\textbf{Professional Activities}}
\vspace{1mm}

\begin{tabular}{l @{\hspace{4.5ex}} l }
2020-2023 & Northwestern University Economics Ph.D. Mentorship Program \\
2021 & Northwestern University Development Lunch Seminar Organizer
\end{tabular}
\vspace{2mm}
\hfill{}
\vspace{1mm}



\end{document}